\vspace{-2cm}A generative model for urban firm networks

### 2020-09-11 CoverLetter.tex
Update on Overleaf.

\justify
We are pleased, with my co-authors Natalia Zdanowska (University College London) and Elsa Arcaute (University College London), to submit an original research article entitled ``Modeling growth of urban firm networks'' for consideration for publication in PLoS ONE. This article introduces a generative model for urban firm networks, to understand underlying processes and with possible application to policies. It does not contain previously published work. Preliminary results were presented as a satellite abstract at the Conference on Complex Systems 2019 (September 2019) and will be presented as a main track abstract at the NetScience 2020 conference (September 2020). We did not have any previous interaction with PLOS regarding this manuscript.

This manuscript has not been published and is not under consideration for publication elsewhere. A preprint was deposited on arxiv simultaneously to the submission.

We have no conflicts of interest to disclose. We do not have any opposed reviewer. This paper is submitted to the PloS ONE collection ``Cities as Complex Systems'' edited by M. Gonzalez (University of California, Berkeley) and D. Rybski (Potsdam Institute for Climate Impact Research).

>>>>

\justify
We are pleased, with my co-authors Natalia Zdanowska (University College London) and Elsa Arcaute (University College London), to submit an original research article entitled ``Modeling growth of urban firm networks'' for consideration for publication in PLoS ONE. This article introduces a generative model for urban firm networks, to understand underlying processes, with possible applications to public policies. %It does not contain previously published work. Preliminary results were presented as a satellite abstract at the Conference on Complex Systems 2019 (September 2019) and will be presented as a main track abstract at the NetScience 2020 conference (September 2020). We did not have any previous interaction with PLoS regarding this manuscript.

This manuscript has not been published and is not under consideration for publication elsewhere, nor contains previously published work. A preprint is being deposited on arxiv simultaneously to the submission.

We have no conflicts of interest to disclose. We do not have any opposed reviewer. This paper is submitted to the PloS ONE collection ``Cities as Complex Systems'' edited by M. Gonzalez (University of California, Berkeley) and D. Rybski (Potsdam Institute for Climate Impact Research). We know that the official deadline has passed, nevertheless, we hope that it could still be considered for this special issue.

### 2020-09-11 main.tex
Update on Overleaf.

%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{figures/Fig1.png}
    \end{center}
    \caption{Distributions of network properties. \textit{(Left)} Cumulated distribution for edge weight, with power law fit (red) and log-normal fit (green); \textit{(Right)} Cumulated distribution for weighted degree.}
    \label{fig:nwdist}
\end{figure}
%%%%%%%%%%%%%

@@

The communities reflect characteristic socio-cultural structures and cross-border economic ties throughout Europe. Cities in France, Belgium and Luxembourg belong to the same cluster as they share French as a common business language, but also cross-border tax arrangements creating easier economic interactions \cite{DecovilleDurand2019}. The same socio-cultural proximity effect is seen in cities of the United Kingdom and Ireland, and those of Sweden, Finland, Estonia, Latvia and Lithuania. The cluster composed of Dutch and Polish cities is justified by the fact that firms from the Netherlands are among the first foreign owners of polish firms since 2010 \cite{2019arXiv191014652Z}. The cluster including cities in Germany, Czech Republic, Austria, Slovakia, Hungary and partly in Romania, find its origin in the dependence of the Central and Eastern European economies on German and Austrian large companies mostly from the automotive sector (i.e. Audi, Volkswagen). In addition, all cities of the later cluster have in common to be at the intersection of a very important freight transport route in Europe from Germany to Turkey \cite{Zdanowska2017}. 
%%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
    \includegraphics[width=\linewidth]{figures/Fig2.png}
    \end{center}
    \caption{{\bf Map of network communities obtained by modularity maximisation.} The area of circles gives the turnover within the Functional Urban Area, and color the community it belongs to. Urban Areas in communities of size smaller than 3 were not colored for readability.}
    \label{fig:fig2}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in}
\caption{{\bf Statistical models.} Ordinary Least Square estimations of statistical models explaining $\log(w_{ij})$ (standard errors in parenthesis). ***, ** and * respectively indicate 0.01, 0.05 and 0.1 levels of significance. For the fixed effect by origin-destination pairs of countries, the proportion of significant coefficients is attributed (where $p<0.1$). Models (1) to (4) are ordinary least square models, while model (5) is a Poisson generalized linear model with logarithmic link. We compare model performance using $R^2$, Mean Square Error, and Akaike Information Criterion. For the Poisson model (model 5), AIC is not given as it is not comparable. \label{tab:reg}}
\medskip
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Model  & (1) & (2) & (3) & (4) & (5) \\ 
\hline
$\log(d_{ij})$ &      -0.06** (0.03) &   -0.11** (0.05)  & -0.41*** (0.02)  & -0.35*** (0.04)  &  -0.26*** ($5\cdot 10^{-6}$) \\
$\log(T_i)$ &   &   & 0.56*** (0.01) &  0.56*** (0.01) & 0.79*** ($2\cdot 10^{-6}$) \\
$\log(T_j)$ &     &   & 0.39*** (0.01) &  0.39*** (0.01) & 0.66***  ($1.5\cdot 10^{-6}$) \\
$\log(s_{ij})$ &     &   &  &  0.19*** (0.07) & 0.53*** ($9\cdot 10^{-6}$)  \\
Countries &    &  28.3\% &   &  26.5\% & 100\% \\
\hline
$R^2$ &       0.00059   &  0.17 & 0.21 &  0.31  &  0.56 \\
MSE & 7.75 & 6.84 & 6.10 & 5.33 & 8.72 \\
AIC &        44304   &  43578  &  42131  & 41917 &   \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{figures/Fig3.png}
    \end{center}
    \caption{Example of simulated networks at $t=1500$, for a synthetic system of cities (Top row) and the European urban network (Bottom row), with a high (resp. low) gravity decay parameter for the left column (resp. right).\label{fig:fig3}}
\end{figure}
%%%%%%%%%%%%%

@@

A global sensitivity analysis first unveils an aggregated influence of parameters on model indicators. We apply Saltelli's Global Sensitivity method introduced by \cite{saltelli2008global}. This produces values for each parameter and each output of a first order sensitivity index, defined as $Var\left[\mathbb{E}_{\mathbf{X}_{\sim i}}\left(Y_j | X_i\right)\right] / Var\left[Y_j\right]$, for parameter $X_i$ and output $Y_j$, $\mathbf{X}_{\sim i}$ being all other parameters. This captures the total influence of $X_i$ all other things being equal. The total order index is given by $\mathbb{E}_{\mathbf{X}_{\sim i}} \left[Var(Y_j | \mathbf{X}_{\sim i})\right] / Var\left[Y_j\right]$ and captures non-homogeneity in behavior and interaction between parameters. Indices were estimated with a Sobol sequence sampling of 20,000 model runs \cite{saltelli2010variance}. We give in \ref{S4_Text} the full estimated results. To summarize, we find that indicators related to modularity (internationalisation and optimal modularity) are mostly influenced by geographical parameters. On the contrary, indicators of network structure are driven by origin and destination sizes. The influence of sectors and historical links has a secondary but not negligible role. Altogether, the analysis witnesses of strong interaction effects between parameters, since for several indicators the total order index is one order of magnitude larger than the first order index. This means that the generative model captures some complex behavior of the system.

@@

%%%%%%%%%%%%%
\begin{figure}
	\begin{center}
	    \includegraphics[width=\linewidth]{figures/Fig4.png}
	\end{center}
    \caption{(Top Left) Internationalisation index decreases exponentially with gravity decay; (Top Right) Correlation between city weighted degree and size. Both plots show a transition from a local to a global regime. (Bottom Left) Internationalisation varies linearly with sector proximity $\gamma_S$; (Bottom Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important. \label{fig:fig4}}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/Fig5.png}
    \caption{The transition as a function of interaction range depends on the influence of origin size $\gamma_O$; sector proximity $\gamma_S$ plays a role only for a large influence of the origin.\label{fig:fig5}}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=\textwidth]{figures/Fig6.png}
	\caption{Maximal integration in terms of community size is achieved at an intermediate value of d$_o$: emergence of a regional regime; maximal size depends on the role of sectors $\gamma_S$ in a decreasing way when the origin size is deactivated, and in an increasing way when $\gamma_o=1$; this regime disappears when the influence of the origin size becomes too large.\label{fig:fig6}}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{figures/Fig7.png}
    \end{center}
    \caption{\textbf{Impact of urban hierarchy.} (Left) Internationalisation as a function of the initial synthetic hierarchy $\alpha$, for different values of interaction range $d_0$ (color); (Right) Metropolisation as a function of $\alpha$, for different values of interaction range $d_0$ (color).\label{fig:fig7}}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
	\begin{center}
    \includegraphics[width=0.75\linewidth]{figures/Fig8.png}
    \end{center}
	\caption{\textbf{Model calibration results.} Pareto front obtained for the bi-objective model calibration for $\varepsilon_L$ and $\varepsilon_M$ objectives. $\varepsilon_L$ can be compared to the MSE of statistical models fitted above, and the generative model outperform these for several parametrizations (lowest MSE 5.33 for statistical models). Point size gives the number of stochastic samples and color the value of $\gamma_O$.\label{fig:fig8}}
\end{figure}
%%%%%%%%%%%%%%

@@

\subsection*{Application: impact of economic shock}

We finally design scenarios to evaluate the impact of economic shocks. These can be the consequence of diverse factors, including socio-economic, geopolitical factors (example of Brexit), or other unpredicted human disasters such as the COVID-19 pandemic. We simulate border closures by rescaling $c_0$, and intra-country lock-downs by rescaling $d_0$ during the simulation, with other parameters being fixed to their default values and the model setup in the real configuration. More precisely, with $t_f = 5000$, the model is run for $t_f / 2$ steps when parameters are changed as $\kappa_G \cdot d_0$ and $\kappa_C \cdot c_0$, and then run for the remaining time steps. We study the temporal trajectory of indicators to see the impact of the shock in time. The experiment is run for $(\kappa_G,\kappa_C)$ ranging between 0.2 (strong restrictions) to 1 (reference trajectory), with 100 model repetitions.

Results are shown in Fig.~\ref{fig:fig9}. We find an important impact of the shock on internationalisation, but less on the average community size. The impact of changing $d_0$ is more important than $c_0$, but a combination of both yield the stronger effect. For minimal values of $\kappa_G$ and $\kappa_C$, internationalisation is more than doubled, confirming a reconfiguration of urban networks within countries. We confirm the statistical significance of effects observed in Fig.~\ref{fig:fig9} by comparing distributions with Kolmogorov-Smirnov (KS) tests. More precisely, we proceed for each indicator and each value of $(\kappa_G,\kappa_C)$ to a two-sided KS test between the statistical distribution of the indicator over repetitions at final time with the distribution in the reference configuration. For internationalisation, p-values of the test are all smaller than 0.002 for $\kappa_D < 0.6$ but all larger than $0.15$ for $\kappa_D \geq 0.6$, what means that the shock has a statistically significant impact only when interaction range is more than halved. For community size, significance (p-value smaller than 0.01) is reached only for the smallest value $\kappa_D = 0.2$. Thus, the trajectory of the urban network is rather resilient to moderate shocks. This application shows how the model could be applied to practical policy issues.

@@

%%%%%%%%%%%%%%
\begin{figure}
	\begin{center}
    \includegraphics[width=\linewidth]{figures/Fig9.png}
    \end{center}
	\caption{\textbf{Application of the calibrated model to an economic shock scenario.} All plots show the trajectory of indicators (internationalisation for the top row and average community size for the bottom row) in time, for different values of interaction decay rescaling $\kappa_G$ (color) and socio-economic distance rescaling $\kappa_C$ (panels). The vertical dotted red line shows the moment the economic shock is introduced and $d_0$ (respectively $c_0$) is set to $\kappa_G \cdot d_0$ (resp. $\kappa_C \cdot c_0$).\label{fig:fig9}}
\end{figure}
%%%%%%%%%%%%%%

@@

The calibration of model suggests its potential application to policy issues and can therefore have practical applications in the future. For example the effect of exogenous shocks in the socio-economic structure can be tested as we did in the stylized application example above. Such shocks can for example be the upcoming impact of Brexit on the European market or the consequence of a long-term closure of the European Union members' borders due to further pandemic outbreaks on the single market. In this sense the UK economic sectors mostly dependent on foreign capital and generating the highest turnovers in 2018 could be examined: extraction of crude petroleum, manufacture of tobacco products and of basic pharmaceutical goods (in terms of out-going links from the UK) ; activities of head offices and holding companies, sale of cars and manufacture of motor vehicles (in terms of in-going links to the UK). We showed in our experiment that although the system is resilient to moderate shocks, strong restrictions have an important impact on internationalization and thus can be expected to have a detrimental effect on UK economy due to these foreign dependency links (see also S1 Text).

>>>>

%%%%%%%%%%%%%
\begin{figure}
    %\begin{center}
    %    \includegraphics[width=\linewidth]{figures/Fig1.png}
    %\end{center}
    \vspace{2cm}
    \caption{Distributions of network properties. \textit{(Left)} Cumulated distribution for edge weight, with power law fit (red) and log-normal fit (green); \textit{(Right)} Cumulated distribution for weighted degree.}
    \label{fig:nwdist}
\end{figure}
%%%%%%%%%%%%%

@@

The communities reflect characteristic socio-cultural structures and cross-border economic ties throughout Europe. Cities in France, Belgium and Luxembourg belong to the same cluster as they share French as a common business language, but also cross-border tax arrangements creating easier economic interactions \cite{DecovilleDurand2019}. The same socio-cultural proximity effect is seen in cities of the United Kingdom and Ireland, and those of Sweden, Finland, Estonia, Latvia and Lithuania. The cluster composed of Dutch and Polish cities is justified by the fact that firms from the Netherlands are among the first foreign owners of polish firms since 2010 \cite{2019arXiv191014652Z}. The cluster including cities in Germany, Czech Republic, Austria, Slovakia, Hungary and partly in Romania, find its origin in the dependence of the Central and Eastern European economies on German and Austrian large companies mostly from the automotive sector (i.e. Audi, Volkswagen). In addition, all cities of the later cluster have in common to be at the intersection of a very important freight transport route in Europe from Germany to Turkey \cite{Zdanowska2017}. 
%%%%%%%%%%%%%%
\begin{figure}
    %\begin{center}
    %\includegraphics[width=\linewidth]{figures/Fig2.png}
    %\end{center}
    \vspace{2cm}
    \caption{{\bf Map of network communities obtained by modularity maximisation.} The area of circles gives the turnover within the Functional Urban Area, and color the community it belongs to. Urban Areas in communities of size smaller than 3 were not colored for readability.}
    \label{fig:fig2}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{table}[!ht]
\begin{adjustwidth}{-1in}{0in}
\caption{{\bf Statistical models.} Ordinary Least Square estimations of statistical models explaining $\log(w_{ij})$ (standard errors in parenthesis). ***, ** and * respectively indicate 0.01, 0.05 and 0.1 levels of significance. For the fixed effect by origin-destination pairs of countries, the proportion of significant coefficients is attributed (where $p<0.1$). Models (1) to (4) are ordinary least square models, while model (5) is a Poisson generalized linear model with logarithmic link. We compare model performance using $R^2$, Mean Square Error, and Akaike Information Criterion. For the Poisson model (model 5), AIC is not given as it is not comparable. \label{tab:reg}}
\medskip
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Model  & (1) & (2) & (3) & (4) & (5) \\ 
\hline
$\log(d_{ij})$ &      -0.06** (0.03) &   -0.11** (0.05)  & -0.41*** (0.02)  & -0.35*** (0.04)  &  -0.26*** ($5\cdot 10^{-6}$) \\
$\log(T_i)$ &   &   & 0.56*** (0.01) &  0.56*** (0.01) & 0.79*** ($2\cdot 10^{-6}$) \\
$\log(T_j)$ &     &   & 0.39*** (0.01) &  0.39*** (0.01) & 0.66***  ($1.5\cdot 10^{-6}$) \\
$\log(s_{ij})$ &     &   &  &  0.19*** (0.07) & 0.53*** ($9\cdot 10^{-6}$)  \\
Countries &    &  28.3\% &   &  26.5\% & 100\% \\
\hline
$R^2$ &       0.00059   &  0.17 & 0.21 &  0.31  &  0.56 \\
MSE & 7.75 & 6.84 & 6.10 & 5.33 & 8.72 \\
AIC &        44304   &  43578  &  42131  & 41917 &   \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
    %\begin{center}
    %    \includegraphics[width=\linewidth]{figures/Fig3.png}
    %\end{center}
    \vspace{2cm}
    \caption{Example of simulated networks at $t=1500$, for a synthetic system of cities (Top row) and the European urban network (Bottom row), with a high (resp. low) gravity decay parameter for the left column (resp. right).\label{fig:fig3}}
\end{figure}
%%%%%%%%%%%%%

@@

A global sensitivity analysis first unveils an aggregated influence of parameters on model indicators. We apply Saltelli's Global Sensitivity method introduced by \cite{saltelli2008global}. This produces values for each parameter and each output of a first order sensitivity index, defined as $Var\left[\mathbb{E}_{\mathbf{X}_{\sim i}}\left(Y_j | X_i\right)\right] / Var\left[Y_j\right]$, for parameter $X_i$ and output $Y_j$, $\mathbf{X}_{\sim i}$ being all other parameters. This captures the total influence of $X_i$ all other things being equal. The total order index is given by $\mathbb{E}_{\mathbf{X}_{\sim i}} \left[Var(Y_j | \mathbf{X}_{\sim i})\right] / Var\left[Y_j\right]$ and captures non-homogeneity in behavior and interaction between parameters. Indices were estimated with a Sobol sequence sampling of 20,000 model runs \cite{saltelli2010variance}. We give in S2 Text the full estimated results for sensitivity indices. To summarize, we find that indicators related to modularity (internationalisation and optimal modularity) are mostly influenced by geographical parameters. On the contrary, indicators of network structure are driven by origin and destination sizes. The influence of sectors and historical links has a secondary but not negligible role. Altogether, the analysis witnesses of strong interaction effects between parameters, since for several indicators the total order index is one order of magnitude larger than the first order index. This means that the generative model captures some complex behavior of the system.

@@

%%%%%%%%%%%%%
\begin{figure}
	%\begin{center}
	%    \includegraphics[width=\linewidth]{figures/Fig4.png}
	%\end{center}
	\vspace{2cm}
    \caption{(Top Left) Internationalisation index decreases exponentially with gravity decay; (Top Right) Correlation between city weighted degree and size. Both plots show a transition from a local to a global regime. (Bottom Left) Internationalisation varies linearly with sector proximity $\gamma_S$; (Bottom Right) Correlation between degree and size exhibits a maximum, witnessing an intermediate regime where size is the most important. \label{fig:fig4}}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    %\includegraphics[width=\linewidth]{figures/Fig5.png}
    \vspace{2cm}
    \caption{The transition as a function of interaction range depends on the influence of origin size $\gamma_O$; sector proximity $\gamma_S$ plays a role only for a large influence of the origin.\label{fig:fig5}}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    %\includegraphics[width=\textwidth]{figures/Fig6.png}
    \vspace{2cm}
	\caption{Maximal integration in terms of community size is achieved at an intermediate value of d$_o$: emergence of a regional regime; maximal size depends on the role of sectors $\gamma_S$ in a decreasing way when the origin size is deactivated, and in an increasing way when $\gamma_o=1$; this regime disappears when the influence of the origin size becomes too large.\label{fig:fig6}}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
    %\begin{center}
    %    \includegraphics[width=\linewidth]{figures/Fig7.png}
    %\end{center}
    \vspace{2cm}
    \caption{\textbf{Impact of urban hierarchy.} (Left) Internationalisation as a function of the initial synthetic hierarchy $\alpha$, for different values of interaction range $d_0$ (color); (Right) Metropolisation as a function of $\alpha$, for different values of interaction range $d_0$ (color).\label{fig:fig7}}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
	%\begin{center}
    %\includegraphics[width=0.75\linewidth]{figures/Fig8.png}
    %\end{center}
    \vspace{2cm}
	\caption{\textbf{Model calibration results.} Pareto front obtained for the bi-objective model calibration for $\varepsilon_L$ and $\varepsilon_M$ objectives. $\varepsilon_L$ can be compared to the MSE of statistical models fitted above, and the generative model outperform these for several parametrizations (lowest MSE 5.33 for statistical models). Point size gives the number of stochastic samples and color the value of $\gamma_O$.\label{fig:fig8}}
\end{figure}
%%%%%%%%%%%%%%

@@

\section*{Application: impact of economic shock}

We finally design scenarios to evaluate the impact of economic shocks. These can be the consequence of diverse factors, including socio-economic, geopolitical factors (example of Brexit), or other unpredicted human disasters such as the COVID-19 pandemic. We simulate border closures by rescaling $c_0$ -- the range parameter for socio-economic interactions --, and intra-country lock-downs by rescaling $d_0$ -- the range parameter for direct interactions -- during the simulation, with other parameters being fixed to their default values and the model setup in the real configuration. More precisely, with $t_f = 5000$, the model is run for $t_f / 2$ steps. Then, following two new rate parameters $\kappa_C \in \left[0;1\right]$ and $\kappa_G \in \left[0;1\right]$ defining the shock, model parameters are updated as $\kappa_G \cdot d_0$ and $\kappa_C \cdot c_0$. The model is then run for the remaining time steps until $t_f$. We study the temporal trajectory of indicators to see the impact of the shock in time. The experiment is run for $(\kappa_G,\kappa_C)$ ranging between 0.2 (strong restrictions) to 1 (reference trajectory), with 100 model repetitions.

Results are shown in Fig.~\ref{fig:fig9}. We find an important impact of the shock on internationalisation, but less on the average community size. The impact of changing $d_0$ is more important than $c_0$, but a combination of both yield the stronger effect. For minimal values of $\kappa_G$ and $\kappa_C$, internationalisation is more than doubled, confirming a reconfiguration of urban networks within countries. We validate the statistical significance of effects observed in Fig.~\ref{fig:fig9} by comparing distributions with Kolmogorov-Smirnov (KS) tests. More precisely, we proceed for each indicator and value of $(\kappa_G,\kappa_C)$ to a two-sided KS test between the statistical distribution of the indicator over repetitions at final time with the distribution in the reference configuration. For internationalisation, p-values of the test are all smaller than 0.002 for $\kappa_D < 0.6$ but larger than $0.15$ for $\kappa_D \geq 0.6$. This means that the shock has a statistically significant impact only when interaction range is more than halved. For community size, significance (p-value smaller than 0.01) is reached only for the smallest value $\kappa_D = 0.2$. Thus, the trajectory of the urban network is rather resilient to moderate shocks. This application shows how the model could be applied to practical policy issues.

@@

%%%%%%%%%%%%%%
\begin{figure}
	%\begin{center}
    %\includegraphics[width=\linewidth]{figures/Fig9.png}
    %\end{center}
    \vspace{2cm}
	\caption{\textbf{Application of the calibrated model to an economic shock scenario.} All plots show the trajectory of indicators (internationalisation for the top row and average community size for the bottom row) in time, for different values of interaction decay rescaling $\kappa_G$ (color) and socio-economic distance rescaling $\kappa_C$ (panels). The vertical dotted red line shows the moment the economic shock is introduced and $d_0$ (respectively $c_0$) is set to $\kappa_G \cdot d_0$ (resp. $\kappa_C \cdot c_0$).\label{fig:fig9}}
\end{figure}
%%%%%%%%%%%%%%

@@

The calibration of model suggests its potential application to policy issues and can therefore have practical applications in the future. For example the effect of exogenous shocks in the socio-economic structure can be tested as we did in the stylized application example above. Such shocks can for example be the upcoming impact of Brexit on the European market or the consequence of a long-term closure of the European Union members' borders due to further pandemic outbreaks on the single market. In this sense the UK economic sectors mostly dependent on foreign capital and generating the highest turnovers in 2018, that would be the most affected and worth examining in details are: extraction of crude petroleum, manufacture of tobacco products and of basic pharmaceutical goods (in terms of out-going links from the UK) ; activities of head offices and holding companies, sale of cars and manufacture of motor vehicles (in terms of in-going links to the UK). We showed in our experiment that although the system is resilient to moderate shocks, strong restrictions have an important impact on internationalization and thus can be expected to have a detrimental effect on UK economy due to these foreign ownership links (see also S1 Text).
